---
title: "A New Class of Skewed Tensor Distributions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A New Class of Skewed Tensor Distributions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(kableExtra)
options(knitr.table.format = 'markdown')
```

Inkoo Lee

Last Updated - April 24, 2022

## Paper 

- Lee, I., Sinha, D., Mai, Q. & Bandyopadhyay, D. (2021+). *A New Class of Skewed Tensor Distributions.* [[Github]](https://github.com/InkooLee/BSTT)


## Skewed tensor response model
For an order-$K$ tensor response $\mathcal{Y}_i \in \mathbb{R}^{d_1 \times \cdots \times d_K}$ with a vector of covariates $\textbf{x}_i \in \mathbb{R}^p$, we consider a tensor response regression model 
\begin{equation}\label{eq1}
    \mathcal{Y}_{i} = \mathcal{B}\bar{\times}_{(K+1)} \textbf{x}_{i} + \mathcal{E}_{i},~~for~~ i=1,\ldots,n,~ 
\end{equation}
where $\mathcal{B} \in \mathbb{R}^{d_1 \times \cdots \times d_K \times p}$ is an order-$(K+1)$ unknown tensor of regression coefficients, $\bar{\times}_{(K+1)}$ is the $(K+1)$-mode vector product, and the error $\mathcal{E}_{i} \in \mathbb{R}^{d_1 \times \cdots \times d_K}$ is an order-$K$ tensor. We model the skewness in 
the distribution of $\mathcal{Y}$ via 
\begin{equation}\label{eq2}
 \mathcal{E}_{i} = |\mathcal{Z}_{2i}|\times_{K} \pmb{\Lambda} + \mathcal{Z}_{1i}, 
\end{equation}
where $\pmb{\Lambda} = diag(\lambda_1,\ldots,\lambda_{d_K}) \in \mathbb{R}^{d_K \times d_K}$ with skewness parameters $\pmb{\lambda}=(\lambda_1,\ldots,\lambda_{d_K})$ and $|\mathbf{M}|$ denotes the
matrix whose each element of is the absolute value of the corresponding element of matrix $\mathbf{M}$. 

## Tensor Spike-and-Slab Lasso prior
To address the desired dimension reduction of the regression coefficient tensor $\mathcal{B}$ 
while ensuring practical clinical interpretation 
of covariate effects, we use $\beta_{i_1i_2i_3j} = \eta_{i_3j} + \alpha_{i_1i_2i_3j}$ to split 
the effect of $j$-th covariate $x_j$ into overall effects $\eta_{1j}$ and $\eta_{2j}$ on two biomarkers and the difference 
$\alpha_{i_1i_2i_3j}$ of the effect of $x_j$ on 
biomarker $i_3$ from site $i_2$ of tooth $i_1$.
We use a common independent $ \textit{N}(0,\tau^2)$ prior for each $\eta_{i_3j}$ and an 
independent spike-and-slab lasso based sparsity inducing prior \citep{rovckova2018spike}  
for tensor $\mathcal{A}\in \mathbb{R}^{28\times 6\times 2\times 6}$ with elements 
$\alpha_{i_1i_2i_3j}$ as
\begin{equation}\label{eq:TSSL}
\begin{aligned}
    &\alpha_{i_1i_2i_3j} \overset{iid}{\sim} (1-\omega_{i_1i_2i_3j})\psi(\alpha_{i_1i_2i_3j}\mid\gamma_0) + \omega_{i_1i_2i_3j}\psi(\alpha_{i_1i_2i_3j}\mid\gamma),\\
       & \omega_{i_1i_2i_3j}\overset{iid}\sim \textit{Bernoulli}(\phi),
\end{aligned}
\end{equation}
where $\gamma_0\ll\gamma_1$ and $\psi(u\mid\gamma) = (\gamma/2)\textnormal{exp}(-\gamma|u|)$ is the mean-zero Laplace distribution. 
%When $\gamma \ll \gamma_0$, tensor spike-and-slab lasso prior \eqref{eq:TSSL} closely retrieve to tensor spike-and-slab prior. 
The large value of $\phi$ produces highly sparse elements in $\mathcal{A}$. 

## Tensor Normal prior
The alternative choice for $\mathcal{B}$ is tensor normal prior, $\mathcal{B} \sim TN(\textbf{0},b\textbf{I}_{28}$, $b\textbf{I}_6,b\textbf{I}_2,b\textbf{I}_6)$ for some large $b > 0$. 


## GAAD data analysis using `BSTT` package

```{r, eval = FALSE}
## Load package
library(BSTT)
```

We fit the BSTT (Bayesian skewed tensor-$t$) model with tensor spike-and-slab lasso (TSSL) prior.

```{r, eval = FALSE}
# n.burn = burn-in period, n.save = number of posterior samples, thin = thinning size
BSTT_TSSL <- BSTT_TSSL(Y,X,vecy, n.burn = 100, n.save = 1000, thin = 5)
```

### D-Statistic
$D = d_1/|d_2|$ for 
each regression effects $\mathcal{B}_{i_1i_2i_3j}$, where $d_1$ is distance of the Bayesian estimate (posterior median) from null value (0 here) and $d_2$ is the distance of the Bayes estimate from the nearest endpoint of the 95\% CI of the parameter. 
Here, $D > 1.5$ $(D < -1.5)$ implies strong posterior evidence of positive (negative) effect of covariate $x_j$ on the biomarker $i_3$ at site $i_2$ of tooth $i_1$. 
Similarly, the range $-0.8 < D < 0.8$ suggests moderate evidence 
for null hypothesis, and $0.8 \leq  D \leq 1.5$ represents moderate positive effect, and $-1.5 \leq D \leq -0.8$ denotes moderate negative effect of $x_j$ on $\mathcal{Y}_{i_1i_2i_3}$.

The following plot (Figure 2 in the main text) shows D-statistic map of tensor regression coefficients with TSSL prior. 

```{r, echo=FALSE, fig.align='center', fig.width=7, fig.height=3, warning=FALSE}
library(lattice)
setwd("C:/Users/inkku/Downloads")

load("Result_BSTT_TSSL_PPD.rda")
load("Result_BSTT_TSSL_CAL.rda")

PPD_B.est <- PPD_BSTT_TSSL$B.est[2:6,,]
CAL_B.est <- CAL_BSTT_TSSL$B.est[2:6,,]


PPD2init <- as.matrix(PPD_B.est[1,,])
PPD3init <- as.matrix(PPD_B.est[2,,])
PPD4init <- as.matrix(PPD_B.est[3,,])
PPD5init <- as.matrix(PPD_B.est[4,,])
PPD6init <- as.matrix(PPD_B.est[5,,])


CAL2init <- as.matrix(CAL_B.est[1,,])
CAL3init <- as.matrix(CAL_B.est[2,,])
CAL4init <- as.matrix(CAL_B.est[3,,])
CAL5init <- as.matrix(CAL_B.est[4,,])
CAL6init <- as.matrix(CAL_B.est[5,,])

library(lattice)

t=28;s=6;
Acol.regions <- c("#FF80FFFF","#FFB6C1", "#FFFFFF", "#BFFFFFFF", "#1E90FF")

## PPD AGE ##
CIPPD2 <- matrix(NA,168,3)

for (i in 1:168){
  CIPPD2[i,] <- quantile(PPD2init[i,], c(0.025,0.5,0.975))
}

matrix(CIPPD2[,2]/(CIPPD2[,2] - CIPPD2[,1]),t,s)
PPD2_d1 <- as.matrix(CIPPD2[,2]); PPD2_d2 <- matrix(NA, 168, 1)
for (i in 1:168){
  if (PPD2_d1[i,] > 0){
    PPD2_d2[i,] <- PPD2_d1[i,] - CIPPD2[i,1]
  }
  else {PPD2_d2[i,] <- CIPPD2[i,3] - PPD2_d1[i,]}
}
PPD2map <- PPD2_d1/abs(PPD2_d2)
PPD2map <- matrix(PPD2map, t,s)
min(PPD2map); max(PPD2map)
PPD2map <- levelplot(t(PPD2map),col.regions = Acol.regions,xlab="sites",ylab="teeth", at = c(-100,-4,-3.2,1,1.5,100),
                     colorkey = FALSE, labels=as.character(c(-100,-4,-3.2,1,1.5,100)),
                     margin=F, scales = list(draw = FALSE),main = "PPD_Age")

print(PPD2map, split = c(1, 1, 5, 2), more = TRUE)

## PPD Gender ##
CIPPD3 <- matrix(NA,168,3)

for (i in 1:168){
  CIPPD3[i,] <- quantile(PPD3init[i,], c(0.025,0.5,0.975))
}

PPD3_d1 <- as.matrix(CIPPD3[,2]); PPD3_d2 <- matrix(NA, 168, 1)
for (i in 1:168){
  if (PPD3_d1[i,] > 0){
    PPD3_d2[i,] <- PPD3_d1[i,] - CIPPD3[i,1]
  }
  else {PPD3_d2[i,] <- CIPPD3[i,3] - PPD3_d1[i,]}
}
PPD3map <- PPD3_d1/abs(PPD3_d2)
PPD3map <- matrix(PPD3map, t,s)
min(PPD3map); max(PPD3map); PPD3map[16,6] <- -1.75
PPD3map <- levelplot(t(PPD3map),col.regions = Acol.regions,xlab="sites",ylab="teeth", at = c(-10,-1.5,-0.75,0.75,1.5,4),
                     colorkey = FALSE, labels=as.character(c(-10,-1.5,-0.75,0.75,1.5,4)),
                     margin=F, scales = list(draw = FALSE),main = "PPD_Gender")

print(PPD3map, split = c(2, 1, 5, 2), more = TRUE)

## PPD BMI ##
CIPPD4 <- matrix(NA,168,3)

for (i in 1:168){
  CIPPD4[i,] <- quantile(PPD4init[i,], c(0.025,0.5,0.975))
}


PPD4_d1 <- as.matrix(CIPPD4[,2]); PPD4_d2 <- matrix(NA, 168, 1)
for (i in 1:168){
  if (PPD4_d1[i,] > 0){
    PPD4_d2[i,] <- PPD4_d1[i,] - CIPPD4[i,1]
  }
  else {PPD4_d2[i,] <- CIPPD4[i,3] - PPD4_d1[i,]}
}
PPD4map <- PPD4_d1/abs(PPD4_d2)
PPD4map <- matrix(PPD4map, t,s)
min(PPD4map);max(PPD4map)
PPD4map <- levelplot(t(PPD4map),col.regions = Acol.regions,xlab="sites",ylab="teeth", at = c(-4,-1.5,-0.9,0.9,1.5,4),
                     colorkey = FALSE, labels=as.character(c(-4,-1.5,-0.9,0.9,1.5,4)),
                     margin=F, scales = list(draw = FALSE),main = "PPD_BMI")
print(PPD4map, split = c(3, 1, 5, 2), more = TRUE)



## PPD Smoker ##
CIPPD5 <- matrix(NA,168,3)

for (i in 1:168){
  CIPPD5[i,] <- quantile(PPD5init[i,], c(0.025,0.5,0.975))
}


PPD5_d1 <- as.matrix(CIPPD5[,2]); PPD5_d2 <- matrix(NA, 168, 1)
for (i in 1:168){
  if (PPD5_d1[i,] > 0){
    PPD5_d2[i,] <- PPD5_d1[i,] - CIPPD5[i,1]
  }
  else {PPD5_d2[i,] <- CIPPD5[i,3] - PPD5_d1[i,]}
}
PPD5map <- PPD5_d1/abs(PPD5_d2)
PPD5map <- matrix(PPD5map, t,s)
min(PPD5map);max(PPD5map)
PPD5map <- levelplot(t(PPD5map),col.regions = Acol.regions,xlab="sites",ylab="teeth", at = c(-4,-1.5,-0.8,0.8,1.5,8),
                     colorkey = FALSE, labels=as.character(c(-4,-1.5,-0.8,0.8,1.5,8)),
                     margin=F, scales = list(draw = FALSE),main = "PPD_Smoker")
print(PPD5map, split = c(4, 1, 5, 2), more = TRUE)

## PPD HbA1c ##
CIPPD6 <- matrix(NA,168,3)

for (i in 1:168){
  CIPPD6[i,] <- quantile(PPD6init[i,], c(0.025,0.5,0.975))
}


PPD6_d1 <- as.matrix(CIPPD6[,2]); PPD6_d2 <- matrix(NA, 168, 1)
for (i in 1:168){
  if (PPD6_d1[i,] > 0){
    PPD6_d2[i,] <- PPD6_d1[i,] - CIPPD6[i,1]
  }
  else {PPD6_d2[i,] <- CIPPD6[i,3] - PPD6_d1[i,]}
}
PPD6map <- PPD6_d1/abs(PPD6_d2)
PPD6map <- matrix(PPD6map, t,s)
min(PPD6map);max(PPD6map)
PPD6map <- levelplot(t(PPD6map),col.regions = Acol.regions,xlab="sites",ylab="teeth", at = c(-4,-1.5,-0.8,0.8,1.5,8),
                     colorkey = FALSE, labels=as.character(c(-4,-1.5,-0.8,0.8,1.5,8)),
                     margin=F, scales = list(draw = FALSE),main = "PPD_HbA1c")
print(PPD6map, split = c(5, 1, 5, 2), more = TRUE)


## CAL AGE ##

CICAL2 <- matrix(NA,168,3)

for (i in 1:168){
  CICAL2[i,] <- quantile(CAL2init[i,], c(0.025,0.5,0.975))
}


CAL2_d1 <- as.matrix(CICAL2[,2]); CAL2_d2 <- matrix(NA, 168, 1)
for (i in 1:168){
  if (CAL2_d1[i,] > 0){
    CAL2_d2[i,] <- CAL2_d1[i,] - CICAL2[i,1]
  }
  else {CAL2_d2[i,] <- CICAL2[i,3] - CAL2_d1[i,]}
}
CAL2map <- CAL2_d1/abs(CAL2_d2)
CAL2map <- matrix(CAL2map, t,s)
max(CAL2map);min(CAL2map)
CAL2map <- levelplot(t(CAL2map),col.regions = Acol.regions,xlab="sites",ylab="teeth", at = c(-100,-4,-3.2,1,1.48,100),
                     colorkey = FALSE, labels=as.character(c(-100,-4,-3.2,1,1.48,100)),
                     margin=F, scales = list(draw = FALSE),main = "CAL_Age")

print(CAL2map, split = c(1, 2, 5, 2), more = TRUE)

## CAL Gender ##
CICAL3 <- matrix(NA,168,3)

for (i in 1:168){
  CICAL3[i,] <- quantile(CAL3init[i,], c(0.025,0.5,0.975))
}


CAL3_d1 <- as.matrix(CICAL3[,2]); CAL3_d2 <- matrix(NA, 168, 1)
for (i in 1:168){
  if (CAL3_d1[i,] > 0){
    CAL3_d2[i,] <- CAL3_d1[i,] - CICAL3[i,1]
  }
  else {CAL3_d2[i,] <- CICAL3[i,3] - CAL3_d1[i,]}
}
CAL3map <- CAL3_d1/abs(CAL3_d2)
CAL3map <- matrix(CAL3map, t,s)
min(CAL3map); max(CAL3map)
CAL3map <- levelplot(t(CAL3map),col.regions = Acol.regions,xlab="sites",ylab="teeth", at = c(-10,-1.5,-0.8,0.8,1.5,4),
                     colorkey = FALSE, labels=as.character(c(-10,-1.5,-0.8,0.8,1.5,4)),
                     margin=F, scales = list(draw = FALSE),main = "CAL_Gender")

print(CAL3map, split = c(2, 2, 5, 2), more = TRUE)

## CAL BMI ##
CICAL4 <- matrix(NA,168,3)

for (i in 1:168){
  CICAL4[i,] <- quantile(CAL4init[i,], c(0.025,0.5,0.975))
}


CAL4_d1 <- as.matrix(CICAL4[,2]); CAL4_d2 <- matrix(NA, 168, 1)
for (i in 1:168){
  if (CAL4_d1[i,] > 0){
    CAL4_d2[i,] <- CAL4_d1[i,] - CICAL4[i,1]
  }
  else {CAL4_d2[i,] <- CICAL4[i,3] - CAL4_d1[i,]}
}
CAL4map <- CAL4_d1/abs(CAL4_d2)
CAL4map <- matrix(CAL4map, t,s)
min(CAL4map); max(CAL4map)
CAL4map <- levelplot(t(CAL4map),col.regions = Acol.regions,xlab="sites",ylab="teeth", at = c(-4,-2,-1,1,2,4),
                     colorkey = FALSE, labels=as.character(c(-4,-2,-1,1,2,4)),
                     margin=F, scales = list(draw = FALSE),main = "CAL_BMI")
print(CAL4map, split = c(3, 2, 5, 2), more = TRUE)

## CAL Smoker ##
CICAL5 <- matrix(NA,168,3)

for (i in 1:168){
  CICAL5[i,] <- quantile(CAL5init[i,], c(0.025,0.5,0.975))
}

CAL5_d1 <- as.matrix(CICAL5[,2]); CAL5_d2 <- matrix(NA, 168, 1)
for (i in 1:168){
  if (CAL5_d1[i,] > 0){
    CAL5_d2[i,] <- CAL5_d1[i,] - CICAL5[i,1]
  }
  else {CAL5_d2[i,] <- CICAL5[i,3] - CAL5_d1[i,]}
}
CAL5map <- CAL5_d1/abs(CAL5_d2)
CAL5map <- matrix(CAL5map, t,s)
min(CAL5map);max(CAL5map)
CAL5map <- levelplot(t(CAL5map),col.regions = Acol.regions,xlab="sites",ylab="teeth", at = c(-4,-1.5,-0.8,0.8,1.5,100),
                     colorkey = FALSE, labels=as.character(c(-4,-1.5,-0.8,0.8,1.5,100)),
                     margin=F, scales = list(draw = FALSE),main = "CAL_Smoker")
print(CAL5map, split = c(4, 2, 5, 2), more = TRUE)

## CAL HbA1c ##

CICAL6 <- matrix(NA,168,3)

for (i in 1:168){
  CICAL6[i,] <- quantile(CAL6init[i,], c(0.025,0.5,0.975))
}

CAL6_d1 <- as.matrix(CICAL5[,2]); CAL6_d2 <- matrix(NA, 168, 1)
for (i in 1:168){
  if (CAL6_d1[i,] > 0){
    CAL6_d2[i,] <- CAL6_d1[i,] - CICAL6[i,1]
  }
  else {CAL6_d2[i,] <- CICAL6[i,3] - CAL6_d1[i,]}
}
CAL6map <- CAL6_d1/abs(CAL6_d2)
CAL6map <- matrix(CAL6map, t,s)
min(CAL6map);max(CAL6map)
CAL6map <- levelplot(t(CAL6map),col.regions = Acol.regions,xlab="sites",ylab="teeth", at = c(-4,-1.5,-0.8,0.8,1.25,300),
                     colorkey = FALSE, labels=as.character(c(-4,-1.5,-0.8,0.8,1.3,300)),
                     margin=F, scales = list(draw = FALSE),main = "CAL_HbA1c")
print(CAL6map, split = c(5, 2, 5, 2), more = TRUE)
```

Now, We fit the BSTT model with tensor normal prior.

```{r, echo=FALSE}
BSTT_TN <- BSTT_TN(Y,X,vecy, n.burn = 100, n.save = 1000, thin = 5)
```

```{r, fig.align='center', fig.width=6, fig.height=3}
library(lattice)
setwd("C:/Users/inkku/Downloads")

load("Result_BSTT.rda")

t = 28; s = 6; b = 2;

PPD_B.est <- result$B.est[2:6,1:(t*s),]
dim(PPD_B.est) 

PPD2init <- as.matrix(PPD_B.est[1,,])
PPD3init <- as.matrix(PPD_B.est[2,,])
PPD4init <- as.matrix(PPD_B.est[3,,])
PPD5init <- as.matrix(PPD_B.est[4,,])
PPD6init <- as.matrix(PPD_B.est[5,,])

CAL_B.est <- result$B.est[2:6,(t*s + 1):(t*s*b),]
dim(CAL_B.est)

CAL2init <- as.matrix(CAL_B.est[1,,])
CAL3init <- as.matrix(CAL_B.est[2,,])
CAL4init <- as.matrix(CAL_B.est[3,,])
CAL5init <- as.matrix(CAL_B.est[4,,])
CAL6init <- as.matrix(CAL_B.est[5,,])

Acol.regions <- c("#FF80FFFF","#FFB6C1", "#FFFFFF", "#BFFFFFFF", "#1E90FF")

## PPD AGE ##
CIPPD2 <- matrix(NA,168,3)

for (i in 1:168){
  CIPPD2[i,] <- quantile(PPD2init[i,], c(0.025,0.5,0.975))
}

PPD2_d1 <- as.matrix(CIPPD2[,2]); PPD2_d2 <- matrix(NA, 168, 1)
for (i in 1:168){
  if (PPD2_d1[i,] > 0){
    PPD2_d2[i,] <- PPD2_d1[i,] - CIPPD2[i,1]
  }
  else {PPD2_d2[i,] <- CIPPD2[i,3] - PPD2_d1[i,]}
}
PPD2map <- PPD2_d1/abs(PPD2_d2)
PPD2map <- matrix(PPD2map, t,s)

PPD2map <- levelplot(t(PPD2map),col.regions = Acol.regions,xlab="sites",ylab="teeth", at = c(-1000,-1.5,-0.8,0.8,1.5,1000),
                     colorkey = FALSE, labels=as.character(c(-1000,-1.5,-0.8,0.8,1.5,1000)),
                     margin=F, scales = list(draw = FALSE),main = "PPD_Age")

print(PPD2map, split = c(1, 1, 5, 2), more = TRUE)

## PPD Gender ##
CIPPD3 <- matrix(NA,168,3)

for (i in 1:168){
  CIPPD3[i,] <- quantile(PPD3init[i,], c(0.025,0.5,0.975))
}

PPD3_d1 <- as.matrix(CIPPD3[,2]); PPD3_d2 <- matrix(NA, 168, 1)
for (i in 1:168){
  if (PPD3_d1[i,] > 0){
    PPD3_d2[i,] <- PPD3_d1[i,] - CIPPD3[i,1]
  }
  else {PPD3_d2[i,] <- CIPPD3[i,3] - PPD3_d1[i,]}
}
PPD3map <- PPD3_d1/abs(PPD3_d2)
PPD3map <- matrix(PPD3map, t,s)

PPD3map <- levelplot(t(PPD3map),col.regions = Acol.regions,xlab="sites",ylab="teeth", at = c(-1000,-1.5,-0.8,0.8,1.5,1000),
                     colorkey = FALSE, labels=as.character(c(-1000,-1.5,-0.8,0.8,1.5,1000)),
                     margin=F, scales = list(draw = FALSE),main = "PPD_Gender")

print(PPD3map, split = c(2, 1, 5, 2), more = TRUE)

## PPD BMI ##
CIPPD4 <- matrix(NA,168,3)

for (i in 1:168){
  CIPPD4[i,] <- quantile(PPD4init[i,], c(0.025,0.5,0.975))
}

PPD4_d1 <- as.matrix(CIPPD4[,2]); PPD4_d2 <- matrix(NA, 168, 1)
for (i in 1:168){
  if (PPD4_d1[i,] > 0){
    PPD4_d2[i,] <- PPD4_d1[i,] - CIPPD4[i,1]
  }
  else {PPD4_d2[i,] <- CIPPD4[i,3] - PPD4_d1[i,]}
}
PPD4map <- PPD4_d1/abs(PPD4_d2)
PPD4map <- matrix(PPD4map, t,s)

PPD4map <- levelplot(t(PPD4map),col.regions = Acol.regions,xlab="sites",ylab="teeth", at = c(-1000,-1.5,-0.8,0.8,1.5,1000),
                     colorkey = FALSE, labels=as.character(c(-1000,-1.5,-0.8,0.8,1.5,1000)),
                     margin=F, scales = list(draw = FALSE),main = "PPD_BMI")
print(PPD4map, split = c(3, 1, 5, 2), more = TRUE)


## PPD Smoker ##
CIPPD5 <- matrix(NA,168,3)

for (i in 1:168){
  CIPPD5[i,] <- quantile(PPD5init[i,], c(0.025,0.5,0.975))
}

PPD5_d1 <- as.matrix(CIPPD5[,2]); PPD5_d2 <- matrix(NA, 168, 1)
for (i in 1:168){
  if (PPD5_d1[i,] > 0){
    PPD5_d2[i,] <- PPD5_d1[i,] - CIPPD5[i,1]
  }
  else {PPD5_d2[i,] <- CIPPD5[i,3] - PPD5_d1[i,]}
}
PPD5map <- PPD5_d1/abs(PPD5_d2)
PPD5map <- matrix(PPD5map, t,s)

PPD5map <- levelplot(t(PPD5map),col.regions = Acol.regions,xlab="sites",ylab="teeth", at = c(-1000,-1.5,-0.8,0.8,1.5,1000),
                     colorkey = FALSE, labels=as.character(c(-1000,-1.5,-0.8,0.8,1.5,1000)),
                     margin=F, scales = list(draw = FALSE),main = "PPD_Smoker")
print(PPD5map, split = c(4, 1, 5, 2), more = TRUE)

## PPD HbA1c ##
CIPPD6 <- matrix(NA,168,3)

for (i in 1:168){
  CIPPD6[i,] <- quantile(PPD6init[i,], c(0.025,0.5,0.975))
}

PPD6_d1 <- as.matrix(CIPPD6[,2]); PPD6_d2 <- matrix(NA, 168, 1)
for (i in 1:168){
  if (PPD6_d1[i,] > 0){
    PPD6_d2[i,] <- PPD6_d1[i,] - CIPPD6[i,1]
  }
  else {PPD6_d2[i,] <- CIPPD6[i,3] - PPD6_d1[i,]}
}
PPD6map <- PPD6_d1/abs(PPD6_d2)
PPD6map <- matrix(PPD6map, t,s)

PPD6map <- levelplot(t(PPD6map),col.regions = Acol.regions,xlab="sites",ylab="teeth", at = c(-1000,-1.5,-0.8,0.8,1.5,1000),
                     colorkey = FALSE, labels=as.character(c(-1000,-1.5,-0.8,0.8,1.5,1000)),
                     margin=F, scales = list(draw = FALSE),main = "PPD_HbA1c")
print(PPD6map, split = c(5, 1, 5, 2), more = TRUE)


## CAL AGE ##
CICAL2 <- matrix(NA,168,3)

for (i in 1:168){
  CICAL2[i,] <- quantile(CAL2init[i,], c(0.025,0.5,0.975))
}

CAL2_d1 <- as.matrix(CICAL2[,2]); CAL2_d2 <- matrix(NA, 168, 1)
for (i in 1:168){
  if (CAL2_d1[i,] > 0){
    CAL2_d2[i,] <- CAL2_d1[i,] - CICAL2[i,1]
  }
  else {CAL2_d2[i,] <- CICAL2[i,3] - CAL2_d1[i,]}
}
CAL2map <- CAL2_d1/abs(CAL2_d2)
CAL2map <- matrix(CAL2map, t,s)

CAL2map <- levelplot(t(CAL2map),col.regions = Acol.regions,xlab="sites",ylab="teeth", at = c(-1000,-1.5,-0.8,0.8,1.5,1000),
                     colorkey = FALSE, labels=as.character(c(-1000,-1.5,-0.8,0.8,1.5,1000)),
                     margin=F, scales = list(draw = FALSE),main = "CAL_Age")

print(CAL2map, split = c(1, 2, 5, 2), more = TRUE)

## CAL Gender ##
CICAL3 <- matrix(NA,168,3)

for (i in 1:168){
  CICAL3[i,] <- quantile(CAL3init[i,], c(0.025,0.5,0.975))
}

CAL3_d1 <- as.matrix(CICAL3[,2]); CAL3_d2 <- matrix(NA, 168, 1)
for (i in 1:168){
  if (CAL3_d1[i,] > 0){
    CAL3_d2[i,] <- CAL3_d1[i,] - CICAL3[i,1]
  }
  else {CAL3_d2[i,] <- CICAL3[i,3] - CAL3_d1[i,]}
}
CAL3map <- CAL3_d1/abs(CAL3_d2)
CAL3map <- matrix(CAL3map, t,s)

CAL3map <- levelplot(t(CAL3map),col.regions = Acol.regions,xlab="sites",ylab="teeth", at = c(-1000,-1.5,-0.8,0.8,1.5,1000),
                     colorkey = FALSE, labels=as.character(c(-1000,-1.5,-0.8,0.8,1.5,1000)),
                     margin=F, scales = list(draw = FALSE),main = "CAL_Gender")

print(CAL3map, split = c(2, 2, 5, 2), more = TRUE)

## CAL BMI ##
CICAL4 <- matrix(NA,168,3)

for (i in 1:168){
  CICAL4[i,] <- quantile(CAL4init[i,], c(0.025,0.5,0.975))
}

CAL4_d1 <- as.matrix(CICAL4[,2]); CAL4_d2 <- matrix(NA, 168, 1)
for (i in 1:168){
  if (CAL4_d1[i,] > 0){
    CAL4_d2[i,] <- CAL4_d1[i,] - CICAL4[i,1]
  }
  else {CAL4_d2[i,] <- CICAL4[i,3] - CAL4_d1[i,]}
}
CAL4map <- CAL4_d1/abs(CAL4_d2)
CAL4map <- matrix(CAL4map, t,s)

CAL4map <- levelplot(t(CAL4map),col.regions = Acol.regions,xlab="sites",ylab="teeth", at = c(-1000,-1.5,-0.8,0.8,1.5,1000),
                     colorkey = FALSE, labels=as.character(c(-1000,-1.5,-0.8,0.8,1.5,1000)),
                     margin=F, scales = list(draw = FALSE),main = "CAL_BMI")
print(CAL4map, split = c(3, 2, 5, 2), more = TRUE)

## CAL Smoker ##
CICAL5 <- matrix(NA,168,3)

for (i in 1:168){
  CICAL5[i,] <- quantile(CAL5init[i,], c(0.025,0.5,0.975))
}

CAL5_d1 <- as.matrix(CICAL5[,2]); CAL5_d2 <- matrix(NA, 168, 1)
for (i in 1:168){
  if (CAL5_d1[i,] > 0){
    CAL5_d2[i,] <- CAL5_d1[i,] - CICAL5[i,1]
  }
  else {CAL5_d2[i,] <- CICAL5[i,3] - CAL5_d1[i,]}
}
CAL5map <- CAL5_d1/abs(CAL5_d2)
CAL5map <- matrix(CAL5map, t,s)

CAL5map <- levelplot(t(CAL5map),col.regions = Acol.regions,xlab="sites",ylab="teeth", at = c(-1000,-1.5,-0.8,0.8,1.5,1000),
                     colorkey = FALSE, labels=as.character(c(-1000,-1.5,-0.8,0.8,1.5,1000)),
                     margin=F, scales = list(draw = FALSE),main = "CAL_Smoker")
print(CAL5map, split = c(4, 2, 5, 2), more = TRUE)

## CAL HbA1c ##
CICAL6 <- matrix(NA,168,3)

for (i in 1:168){
  CICAL6[i,] <- quantile(CAL6init[i,], c(0.025,0.5,0.975))
}

CAL6_d1 <- as.matrix(CICAL5[,2]); CAL6_d2 <- matrix(NA, 168, 1)
for (i in 1:168){
  if (CAL6_d1[i,] > 0){
    CAL6_d2[i,] <- CAL6_d1[i,] - CICAL6[i,1]
  }
  else {CAL6_d2[i,] <- CICAL6[i,3] - CAL6_d1[i,]}
}
CAL6map <- CAL6_d1/abs(CAL6_d2)
CAL6map <- matrix(CAL6map, t,s)

CAL6map <- levelplot(t(CAL6map),col.regions = Acol.regions,xlab="sites",ylab="teeth", at = c(-1000,-1.5,-0.8,0.8,1.5,1000),
                     colorkey = FALSE, labels=as.character(c(-1000,-1.5,-0.8,0.8,1.5,1000)),
                     margin=F, scales = list(draw = FALSE),main = "CAL_HbA1c")
print(CAL6map, split = c(5, 2, 5, 2), more = TRUE)
```

Figure shows checkerboard pattern impeding straightforward interpretation.












